Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-08 WRITEUP/ms.tex
edited Q figure caption and some text

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.85\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{
Distributions of mass, size, and gas mass fraction of MCs identified using
the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified
at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

Maps of the gas Toomre $Q$ parameter and the effective two-component $Q_{\rm eff}$ parameter along different projection angles during the accretion phase of \flower are shown in \Fig{Q} and \Fig{Qeff}, respectively (see \Fig{h2density} for examples of clumps identified 
in this snapshot). Fragmentation are expected in regions of low Toomre Q values.
Further interpretation and implication of this is discussed in \Sec{origin}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_0_zoom_1.5_kpc.png}
\caption{
Maps of the total gas surface density (top left), 
velocity dispersion (top right),
epicyclic frequency (bottom left), 
and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
\label{fig:Q}}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/16_gas_toomre_proj_1_zoom_1.5_kpc.png}
\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_gas_toomre_proj_2_zoom_1.5_kpc.png}
\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.85\textwidth]{\figpath/ss16_toomreEff_proj_0_zoom_1.5_kpc.png}
\caption{
Effective two-component Toomre Q map in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
\label{fig:Qeff}}
% \addtocounter{figure}{-1}
\end{figure*}

@@

The apparently large virial parameters seen in the MCs of \flower can be understood using the 
Toomre $Q$ parameter (\Fig{Q} and \Fig{Qeff}). 
We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider 
instability against axisymmetric perturbations), but  
further evolution/collapse depends on the dynamics or equation of state of the gas. 
Such fragmentation is expected to take place at the
critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
Second, this fragmentation scale is greater than the typical size of GMCs. This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs
correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales. 
Thus, the high virial parameter found 
for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure 
and rotation) and surface density, indicate that most of them are not collapsing structures. 
As such, some MCs lie in regions of $Q>1$. 
Only in (the denser) regions with a low Toomre $Q$ parameter and 
when energy can be dissipated on a timescale 
that is shorter than the timescale over which it gains energy (e.g., heating) 
correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$
nature of most MCs of \flower and its relatively high SFR.
That is, if most of the molecular gas in \flower are stable against collapse, 
how does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
The discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by
large-scale gravitational potential and differential rotation.
This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
MCs \citep{Clark04a, Clark05a}.
Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation
and collapse on smaller scales to trigger \SF.

@@

Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter.
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as
result of the weaker stellar feedback as they have
experienced less episodes of \SF compared to \flower 
(also supported by the lower stellar-to-gas mass ratio of the latter).
MCs in the satellites are therefore likely collapsing structures.

>>>>

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.7\textwidth]{\figpath/minmaxNcut_basicDistributions.png}
\caption{
Distributions of mass, size, and gas mass fraction of MCs identified using
the lowest $n_{\rm cut}$ (left panels) and $n_{\rm ncut}$\eq18.96\,\cc (right panels).
Note that the scale shown on the y-axes are different between the left and right panels, as less MCs are identified
at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

@@

Maps of the Toomre $Q$ parameters for the gas, stars, and the effective two-component $Q_{\rm eff}$ are shown in Figures~\ref{fig:Q}, \ref{fig:Qstar}, and \ref{fig:Qeff}, respectively (see \Fig{h2density} for an example of MCs identified 
in this snapshot). Fragmentation are expected in regions of low Toomre $Q$ values.
Further interpretation and implication of this is discussed in \Sec{origin}.

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_0_zoom_2.0_kpc}.png}
\caption{
Maps of the total gas surface density (top left), 
velocity dispersion (top right),
epicyclic frequency (bottom left), 
and Toomre $Q$ parameter (bottom right) in the $xy$-plane.
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
Crosses correspond to positions of MCs identified using the lowest $n_{\rm cut}$. % using 0.32
Positions of sub-MCs are not shown (but see top row of \Fig{Qeff} for an example). 
\label{fig:Q}}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_gas_toomre_proj_1_zoom_2.0_kpc}.png}
\caption{Continued. Maps showing the various quantities projected on the $xz$-plane.}
\addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{{\figpath/ss16_gas_toomre_proj_2_zoom_2.0_kpc}.png}
\caption{Continued. Maps show the various quantities projected on the $yz$-plane.}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 20 30 30, clip, width=0.7\textwidth]{\figpath/{ss16_star_toomre_proj_0_zoom_2.0_kpc}.png}
\caption{
Same as \Fig{Q} but for the stellar component, projected in the $xy$-plane.
\label{fig:Qstar}}
% \addtocounter{figure}{-1}
\end{figure*}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=10 0 100 20, clip, width=0.35\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_0.32}.png}
\includegraphics[trim=30 0 10 20, clip, width=0.425\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_2.0_kpc_6.81}.png}  \\
\includegraphics[trim=10 0 0 10, clip, width=0.425\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_2.0_kpc}.png} \\
\includegraphics[trim=30 25 30 20, clip, width=0.4\textwidth]{\figpath/{ss16_toomreEff_proj_0_zoom_0.8_kpc_6.81}.png}
\includegraphics[trim=10 0 0 0, clip, width=0.38\textwidth]{\figpath/{ss16_gas_SD_proj_0_zoom_0.8_kpc}.png}
\caption{
Effective two-component Toomre $Q_{\rm eff}$ (top row) 
and gas surface density (middle) maps projected onto the $xy$-plane.
Positions of MCs identified using the lowest $n_{\rm cut}$\eq0.32\,cm$^{-3}$ (top left; same as \Fig{Q})
and $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (top right) are overplotted as crosses.
Bottom row: Effective $Q_{\rm eff}$ (left) and gas surface density (right) maps zoomed in on the central 1.5\,kpc region.
Cross markers indicate positions of MCs identified with $n_{\rm cut}$\eq6.81\,cm$^{-3}$ (same as top right).
Modest smoothing has been applied to the maps. 
A divergent colormap is used for the Toomre $Q$ map to facilitate 
identification of regions above and below $\log{Q_{\rm gas}}$\eq0.
Some MCs lie in regions of $\log{Q_{\rm eff}}\gtrsim0$, whereas regions of $\log{Q_{\rm eff}}\lesssim0$ 
are likely gravitationally unstable.
\label{fig:Qeff}}
% \addtocounter{figure}{-1}
\end{figure*}
\clearpage

@@

The apparently large virial parameters seen in the MCs of \flower can be understood using the 
Toomre $Q$ parameter (see Figures~\ref{fig:Q}\,r$-$\,\ref{fig:Qeff}). 
We first note that fragmentation {\it can} happen in regions of low $Q$ (if we only consider 
instability against axisymmetric perturbations), but  
further evolution/collapse depends on the dynamics or equation of state of the gas. 
Such fragmentation is expected to take place at the
critical scale length $\lambda_{\rm crit} < 2 \pi^2 G \Sigma / \kappa^2$.
Second, this fragmentation scale is greater than the typical size of GMCs. This could be interpreted as a result of instability setting the scales for fragmentation, but the star-forming GMCs
correspond to the collapsing, denser, and cooler molecular structures that are on smaller scales. 
Thus, the high virial parameter found 
for most MCs in \flower, which is the ratio between the velocity dispersion (accounts for effect of pressure 
and rotation) and surface density, indicate that most of them are not collapsing structures. 
As such, some MCs lie in regions of $Q>1$. 
Only in (the denser) regions with a low Toomre $Q$ parameter and 
when energy can be dissipated on a timescale 
that is shorter than the timescale over which it gains energy (e.g., heating) 
correspond to star-forming {\it clumps} and {\it cores} with low virial parameters.
This would also (at least partially) explain the seemingly inconsistency between the high $\alpha_{\rm vir}$
nature of most MCs of \flower and its relatively high SFR.
That is, if most of the molecular gas in \flower are stable against collapse, 
how does it sustain its high SFR of $\sim$100\,\Msun\,yr\pmOne?
The discrepancy can be explained in two ways.
First, our results are limited by the resolution of the simulation, such that, in each MC, there
likely exist multiple smaller-scales molecular structures (e.g., clumps and cores),
as in the classical molecular cloud hierarchy. This re-iterates the statement about low $Q$ above.
Second, due to turbulence dissipation on small-scales, such (sub-)structures are no longer supported by
large-scale gravitational potential and differential rotation.
This in turn enables subregions of the MCs to collapse and potentially form OB associations out of these unbound
MCs \citep{Clark04a, Clark05a}.
Additional mechanisms causing non-axisymmetric perturbations (e.g., arms) to the gravitational potential
can also induce orbit crossing, shocks and dissipation in gas, further promoting turbulence dissipation
and collapse on smaller scales to trigger \SF.

@@

Virial analysis indicates that the MC/arms of the main disk of \flower are unbound, but the substructures have lower virial parameter.
This is consistent with the notion that collapsing structures result from gravitational instability within globally stable structures, which are
supported by turbulence and rotation on large scale.
We also find $\alpha_{\rm vir}\approx$\,2 for the MCs in the satellite galaxies, which we interpret as
result of the weaker stellar feedback compared to \flower 
MCs in the satellites are therefore likely collapsing structures.
